Verifying Demonstrations

### 2017-11-24 SystemModel.tex

Each participant who want to be counted must submit a participation proof.
The proof must be associated with the protest, i.e.\ its \(id\), time and 
location.
We use witnesses to associate the proof to the location.
The proof and its witnesses are stored in a set, as there should be only unique 
witnesses.

\begin{frame}
\begin{definition}[Witness]
  A \emph{witness} \(w = (pid, cid, t, l, wid)\) is a tuple where
  \(cid, t, l\) are as in \cref{DefProtest},
  \(pid\) uniquely identifies the protester and \(wid\) uniquely identifies the 
  person who issued the witness.
  We let \(W\) be the set of all witnesses.
\end{definition}
\end{frame}

A subset of the witnesses forms a participation proof for a protester.

\begin{frame}
\begin{definition}[Participation proof]
  A \emph{participation proof} of protester \(i\) participating in protest \(j\) 
  is the set
  \begin{align}
    \nonumber
    p_{i, j} =
    \left\{ (pid, cid, t, l, wid)\in W \mid
    %\right. &
    pid = i, cid = j,
    %\\ & \left.
    t \subseteq t_j, l\subseteq l_j \right\},
  \end{align}
  of all witnesses with the same protester and protest identifiers, witness time 
  interval \(t\) and location \(l\) is within those of the protest \(j\) (i.e.\ 
  \(t_j\) and \(l_j\)).
\end{definition}
\end{frame}

@@

The strength function \(s\) can be used to e.g.\ regulate trust in witnesses.
A trivial example would be for \(s\) to return the number of witnesses and thus 
let \(\theta\) to be the threshold of the number of required witnesses.

>>>>

Each participant who want to be counted must submit a participation proof.
The proof must be associated with the protest, i.e.\ its identifier \(cid\), 
time and location.
We use witnesses to associate the proof to the location by creating a proof 
share.
A witness is only allowed to create one proof share per protester.
The proof and its proof shares are stored in a set, as there should be only 
unique proof shares.

\begin{frame}
\begin{definition}[Participation-proof share]
  A \emph{participation-proof share} \(w = (pid, cid, t, l, wid)\) is a tuple 
  where
  \(cid, t, l\) are as in \cref{DefProtest},
  \(pid\) is unique for a protester and \(cid\) pair, and
  \(wid\) is unique for a witness--protester pair.
  We let \(W\) be the set of all proof shares.
\end{definition}
\end{frame}

A subset of the proof shares forms a participation proof for a protester.

\begin{frame}
\begin{definition}[Participation proof]
  A \emph{participation proof} of protester \(i\) participating in protest \(j\) 
  is the set
  \begin{align}
    \nonumber
    p_{i, j} =
    \left\{ (pid, cid, t, l, wid)\in W \mid
    %\right. &
    pid = i, cid = j,
    %\\ & \left.
    t \subseteq t_j, l\subseteq l_j \right\},
  \end{align}
  of all proof shares with the same protester and protest identifiers, witness 
  time interval \(t\) and location \(l\) is within those of the protest \(j\) 
  (i.e.\ \(t_j\) and \(l_j\)).
\end{definition}
\end{frame}

@@

The strength function \(s\) can be used to e.g.\ regulate trust in 
witnesses.
A trivial example would be for \(s\) to return the number of proof shares (i.e.\ 
witnesses) and thus let \(\theta\) to be the threshold of the number of required 
witnesses.

### 2017-11-24 abstract.tex
Removes WIP comment from abstract, fixes title in security section

% What's the approach?
In this work, we are interested in combining location proofs with electronic 
voting to solve this issue.
Since the parties have incentives to cheat, we require transparency: in 
particular we are aiming at a decentralized scheme that provides verifiability 
and privacy.
More specifically, the scheme should be distributed and not depend on any 
authority.
We need verifiability, which means that every participant can verify that their 
participation has been included --- i.e.\ individual verifiability, to prevent 
Eve from dropping data --- and that anyone can verify the correctness of the 
result --- i.e.\ universal and eligibility verifiability, to prevent any 
malicious actor (e.g. Sybil) from affecting the result.
Eligibility verifiability also requires that the data is time-wise related to 
the event (temporal eligibility), which can be provided by blockchain-like 
structures.
The data must also be related to the location (spatial eligibility), something 
a location proof can achieve.
As all things policital, privacy is critical.
Similar to e-voting schemes, we need to guarantee properties close to vote 
privacy and receipt freeness --- Alice does not want Eve's agents to be able to 
infer that she is critical of Eve.
Finally, the scheme must be scalable to handle large protests (i.e.\ millions 
of participants).

In this talk we will discuss this work in progress and elicit input from the
participants.

>>>>

% What's the approach?
In this work, we are interested in combining location proofs with some 
properties of electronic voting to provide verifiable participation counts.
Since the parties have incentives to cheat, we require transparency: in 
particular we are aiming at a decentralized scheme that provides verifiability 
and privacy.
More specifically, the scheme should be distributed, not depend on any authority 
and it must scale to handle large protests (i.e.\ millions of participants).

In our scheme each participant creates a participation proof with the help of 
other participants.
We use blockchains to commit and timestamp the participation proofs, location 
proofs to prove connection to the physical location.
% What's the result?
The scheme provides verifiability, which means that every participant can verify 
that their participation has been included --- i.e.\ individual verifiability, 
to prevent Eve from dropping data --- and that anyone can verify the correctness 
of the result --- i.e.\ universal and eligibility verifiability, to prevent any 
malicious actor (e.g. Sybil) from affecting the result.
Our scheme is privacy preserving in the sense that it adds no risk to a 
participant that was not already present when not using our scheme.

\keywords{%
  crowd counting;
  protesting;
  electronic voting;
  location proof;
  privacy
}
